Tabsets

### 2024-02-15 paper.qmd
delcom
mone
running

```{r, echo=FALSE, results='asis',warning=F}
presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
textm <- readLines(presm)
cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
```

>>>>

```{r}
knitr::knit_exit()
```

```{r, echo=FALSE, results='asis',warning=F}
#presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
#textm <- readLines(presm)
#cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
```
